### 2011-01-06 proof.pre.tex
Make SIGMA TeX notation use an inclusive upper bound

\documentclass{article}
\usepackage{holtexbasic}
\usepackage{alltt}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}
\section*{Introduction}
First, a warning about one quirky convention.
When I write \HOLtm{SIGMA (\m. f m) (count b)} I mean for the variable $m$ to range from $0$ up to but \emph{not including} $b$.

>>>>

\documentclass{article}
\usepackage{holtexbasic}
\usepackage{alltt}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}
\section*{Introduction}
Update: Contrary to my earlier warning when I write \HOLtm{SIGMA (\m. f m) (count (SUC b))} I now mean for the variable $m$ to range from $0$ up to \emph{and including} $b$, as per the usual convention.
